Soc504 Replication Project Report

### 2015-05-11 replication_report-extensions.Rmd
date change.
start of final version of replication project

---
title: "Replication Report"
author: "Yari & Kyonne" 
date: "April 3, 2015"
output: html_document
---

(1) Replicated table:

@@

# Load packages
suppressPackageStartupMessages(require(dplyr))
suppressPackageStartupMessages(require(tidyr))
suppressPackageStartupMessages(require(pwr)) 
suppressPackageStartupMessages(require(broom))
suppressPackageStartupMessages(require(lsr))
suppressPackageStartupMessages(require(ggplot2))
suppressPackageStartupMessages(require(MBESS))
suppressPackageStartupMessages(require(psych))
suppressPackageStartupMessages(require(car))
suppressPackageStartupMessages(require(MASS))
suppressPackageStartupMessages(require(stargazer))

Liked_Music <- c("21(57%)","16(43%)", "N=72, X^2(1)=8.59, p=0.003, phi=0.35")
Disliked_Music <- c("8(23%)","27(77%)", "")
Condition <- c("AdvertisedPen", "NonAdvertisedPen", "Chi-Square")
Freq_Table = cbind(Condition, Liked_Music, Disliked_Music)
stargazer(Freq_Table, type = "text", title = "Study 3: Frequencies of Pen Choice for Each Conditon & Chi-Square")

@@

(2) Explanation: 
The table above is a reproduction of the frequencies and percentages of subjects' choice for advertised and non-advertised pen in the Liked Music & Disliked Music conditions, respectively, in Study 3. Note that at the bottom of the table is also the chi-square statistic, p-value and effect size (phi) for the data, indicating a medium-sized effect of music condition on pen choice. The table also demonstrates that the frequency of choice in the Disliked Music condition was in the hypothesized direction: Subjects tended to choose the non-advertised pen when made to listen to disliked music in an advertisement. Please note that the data represented above follows the exclusion criteria set forth in the published article. Specifically, any subjects who had participated in a prior version of the study were excluded (two subjects). In addition, 19 subjects were excluded for their so-called "deviant music evaluations". These subjects were foundd to either somewhat dislike the "liked music" (music attiude score below 3) or somewhat like the "disliked music" (music attitude score above 3).

(3) Code for analyses & table:

@@

# Load data
dat <- read.csv("GORN_study3.csv", header = TRUE)
dat <- tbl_df(dat)
#head(dat)
#View(dat)

@@

# Filter out 2 excluded participants who accidentily took study twice in the paper:
dat_e <- dat %>%
  filter(excluded == 0)
#dat_e
#View(dat_e)

@@

# Test whether music condition is independent of pen choice:
# (1 == liked music, 2 == disliked music)
# (0 == not chosen, 1 == chosen)
tbl <- table(dat_e$music, dat_e$chose_advertised_pen) 
tbl

@@

# Power analysis -- Find the power to detect .35 effect size reported in paper:
pwr.chisq.test(w = .39, N = 91, df = 1, sig.level = 0.05, power = NULL)

@@

# Filter out additional 19 Ss with too positive attitudes in "disliked music" condition & too negative attitudes in "liked music" condition:

# Find Cronbach's Alpha for music attitudes scale (for comparison with article):
#dat_music <- dat_e %>%
#  select(att_muz1, att_muz2, att_muz3)
#View(dat_music)
#alpha(dat_music, na.rm = TRUE, delete=TRUE)

# Find mean attitudes for each music condition (for comparison with article): 
#dat_e %>%
#  group_by(music) %>%
#  summarise(avg = mean(c(att_muz1, att_muz2, att_muz3)))

# Add mean attitude column to dataframe:
dat_e <- dat_e %>%
  mutate(avg_att_muz = (att_muz1 + att_muz2 + att_muz3) / 3)
#View(dat_e)

# Check those means (for comparison with article):
#dat_e %>%
#  group_by(music) %>%
#  summarise(avg = mean(avg_att_muz))

# Exclude when average attitude > 3 in disliked cond. or average attitude <3 for liked cond. (1 == liked music, 2 == disliked music)
dat_egood <- dat_e %>%
  filter(music == 1 & avg_att_muz > 3 | music == 2 & avg_att_muz < 3)
#View(dat_egood)

@@

(4.1) Extension A: Graphing the frequency of response & Investigating moderation by gender:

@@

(4.1.1) Code for graph and moderation analyses:

@@

(4.2) Extension B: Investigating the possible moderation of effects by gender, using a logistical regression.

@@

(4.2.1) A quick check of N by gender in data:

@@

(4.2.2) Code for logistical regressions:

@@

```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the table. Further, the "eval = FALSE" parameter was added to the top code chunk to prevent printing of the code.

>>>>

---
title: "Soc504 Replication Project Report"
author: "Yari & Kyonne" 
date: "May 10, 2015"
output: html_document
---

TABLE OF CONTENTS:
1 - Synopsis of report.
2 - Replication of original results.
  2.1 - Image of replicated table.
  2.2 - Explanation/description of table results.
  2.3 - Code for replicated table, chi-square analyses and power analyses.
3 - Extensions.
  3.1 - Extension (A): Frequency graph.
    3.1.1 - Code for graph.
  3.2 - Extension (B): Moderation analysis by gender.
    3.2.1 - Check of cell sizes for each gender.
    3.2.2 - Code for logistic regression for moderation analysis.

(1) Synopsis.
This report encompasses the work done to first replicate, and then extend, the findings of Study 3 from Vermeulen et al. (2014). The authors of the original article wanted to know whether single exposure to a certain kind of music (music that is either widely liked or disliked) will condition participants to choose one pen over another. Specifically, they hypothesize that participants exposed to liked music will be conditioned to choose the pen that was advertised while the music is playing; and likewise, participants exposed to disliked music will be conditioned to choose an alternative pen to the one advertised while the music is playing.

Section (2) details our replication process. We reproduce the single figure from the article, a frequency table for the outcome of interest in Study 3 as well as all the chi-square analyses.

Section (3) comprises our two-part extension process. First, we create a bar graph of the frequencies detailed in the original article's table. Second, we statistically test for any moderation of our results by gender, using subsetting the data by gender and then conducting separate logistic regression analyses. From there, we looked for any differences between men and women in the predicted probability of the key outcome variable (pen choice).

(2.1) Replicated table.
Note: the `echo = FALSE` parameter was added to the below code chunk to prevent printing of the R code that generated the table. See section (2.3) for the full code.

@@

# Load packages:
suppressPackageStartupMessages(require(dplyr))
suppressPackageStartupMessages(require(tidyr))
suppressPackageStartupMessages(require(pwr)) 
suppressPackageStartupMessages(require(broom))
suppressPackageStartupMessages(require(lsr))
suppressPackageStartupMessages(require(ggplot2))
suppressPackageStartupMessages(require(MBESS))
suppressPackageStartupMessages(require(psych))
suppressPackageStartupMessages(require(car))
suppressPackageStartupMessages(require(MASS))
suppressPackageStartupMessages(require(stargazer))

# Derrive table of frequencies:
Liked_Music <- c("21(57%)","16(43%)", "N=72, X^2(1)=8.59, p=0.003, phi=0.35")
Disliked_Music <- c("8(23%)","27(77%)", "")
Condition <- c("AdvertisedPen", "NonAdvertisedPen", "Chi-Square")
Freq_Table = cbind(Condition, Liked_Music, Disliked_Music)
stargazer(Freq_Table, type = "text", title = "Study 3: Frequencies of Pen Choice for Each Conditon & Chi-Square")

@@

(2.2) Explanation.
The table above is a reproduction of the frequencies and percentages of subjects' choice for advertised and non-advertised pen in the Liked Music & Disliked Music conditions, respectively, in Study 3. Note that at the bottom of the table is also the chi-square statistic, p-value and effect size (phi) for the data, indicating a medium-sized effect of music condition on pen choice. The table also demonstrates that the frequency of choice in the Disliked Music condition was in the hypothesized direction: Subjects tended to choose the non-advertised pen when made to listen to disliked music in an advertisement. Please note that the data represented above follows the exclusion criteria set forth in the published article. Specifically, any subjects who had participated in a prior version of the study were excluded (two subjects). In addition, 19 subjects were excluded for their so-called "deviant music evaluations". These subjects were foundd to either somewhat dislike the "liked music" (music attiude score below 3) or somewhat like the "disliked music" (music attitude score above 3).

(2.3) Code for analyses & table.
Note: the 'eval = FALSE' parameter was added to this code chunk to prevent printing of the code.

@@

# Load data
dat <- read.csv("GORN_study3.csv", header = TRUE)
dat <- tbl_df(dat)

@@

# Filter out 2 excluded participants who accidentily took study twice in the paper:
dat_e <- dat %>%
  filter(excluded == 0)

@@

# Test whether music condition is independent of pen choice:
# "music"" variable: (1 == liked music, 2 == disliked music)
# "chose_advertised_pen" variable: (0 == not chosen, 1 == chosen)
tbl <- table(dat_e$music, dat_e$chose_advertised_pen)

@@

# Power analysis -- Find the power to detect the .35 effect size reported in paper:
pwr.chisq.test(w = .39, N = 91, df = 1, sig.level = 0.05, power = NULL)

@@

# Filter out additional 19 Ss with too positive attitudes in "disliked music" condition (reported ratings above 3) & too negative attitudes in "liked music" condition (reported ratings below 3):

# Find Cronbach's Alpha for music attitudes scale (for comparison with article):
dat_music <- dat_e %>%
  select(att_muz1, att_muz2, att_muz3)

alpha(dat_music, na.rm = TRUE, delete=TRUE)

# Find mean attitudes for each music condition (for comparison with article): 
dat_e %>%
  group_by(music) %>%
  summarise(avg = mean(c(att_muz1, att_muz2, att_muz3)))

# Add mean attitude column to dataframe:
dat_e <- dat_e %>%
  mutate(avg_att_muz = (att_muz1 + att_muz2 + att_muz3) / 3)

# Check those means (for comparison with article):
dat_e %>%
  group_by(music) %>%
  summarise(avg = mean(avg_att_muz))

# Exclude when average attitude > 3 in disliked cond. or average attitude < 3 for liked cond. (1 == liked music, 2 == disliked music)
dat_egood <- dat_e %>%
  filter(music == 1 & avg_att_muz > 3 | music == 2 & avg_att_muz < 3)

@@

(3.1) Extension A: Graphing the frequency of responses in each condition.

@@

(3.1.1) Code for graph.

@@

(3.2) Extension B: Investigating the possible moderation of effects by gender, using a logistical regression.

@@

(3.2.1) A quick check of N by gender in data.

@@

(3.2.2) Code for logistical regressions.

@@

```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the table. Further, the 'eval = FALSE' parameter was added to the top code chunk to prevent printing of the code.
